Viscous Transport in Eroding Porous Media

### 2019-05-02 docs/transport/erosion_transport.tex
doing tranposrt paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Barcyentric Quadrature for $v''(x)$}
In order to simulate erosion, we require the deformation gradient which
means that a quadrature rule for $v''(x)$ is required.  Using the same
techniques that are used to compute $v(x)$ and $v'(x)$, a Barycentric
quadrature rule for the second derivative can be constructed using the
identities
{\color{red}
\begin{alignat}{3}
  0 &= \frac{1}{2\pi i}\int_{\Gamma} 
    \frac{2v^-({ y})-2v(x)-2(y-x)v'(x)-(y-x)^2v''(x)}{(y-x)^3}, &&x \in \Omega, \\
  0 &= \frac{1}{2\pi i}\int_{\Gamma}
    \frac{2v^+(y)-2v(x)-2(y-x)v'(x)-(y-a)^{-1}(x-a)(y-x)^2 v''(x)}
    {(y-x)^3} dy, \quad &&x \in \Omega^c.  \label{eqn:Identity}
\end{alignat}
and the quadrature formulations are
\begin{alignat}{3}
  v''(x) &\approx
    \frac{2\sum\limits_{j=1}^N \frac{v_j^- -v(x)-(y_j-x)v'(x)}{(y_j-x)^3}w_j}
    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}, &&x \in \Omega, \\
  v''(x) &\approx \frac{1}{x-a}\frac{2\sum\limits_{j=1}^N
    \frac{v_j^+ -v(x)-(y_j-x)v'(x)}{(y-x)^3}}{\sum\limits_{j=1}^N \frac{(y_j-a)^{-1}}{y_j-x}w_j}
    , \quad &&x \in \Omega^c.  \label{eqn:SecondBary}
\end{alignat}
where $a$ is a point inside the $\Omega$ in equations~\eqref{eqn:Identity} and \eqref{eqn:SecondBary}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Fast Summation Methods}
\label{sec:fmm}
\begin{itemize}
  \item Apply trapezoid rule as a first pass
  \item Efficiently find points that are too close for trapezoid

{\color{red}
To numerically compute the completed double-layer potential, we discretize each of the $M$ bodies with  $N_\iin$ points, and the outer boundary with $N_\out$ points. Let $L_w$ be the length of the boundary of wall and $L_{b}$ be length of the boundary of body where $b=1, \cdots, M$. Here are the criteria to see if two points are too close for trapezoid. For criterion of wall to body,  let $d$ be the minimum distance between wall to a point $x_i$ on the body $b$, we define they are too close when
$$d<\frac{L_{b}}{2\pi} + \alpha_1\frac{L_w}{N_\out}$$
where $\alpha_1$ is a constant. 
For criterion between two bodies, let $d$ be the minimum distance between a point $y_j$ on the body $b_1$ to a point $x_i$ on the body $b_2$, we define they are too close when
$$d<\frac{L_{b_1}}{2\pi}+\frac{L_{b_1}}{2\pi}+\alpha_2\left(\frac{L_{b_1}}{N_\iin}+\frac{L_{b_2}}{N_\iin}\right)$$
where $\alpha_2$ is a constant.

}
  \item Subtract off trapezoid rule directly
  \item Add on Barycentric directly
\end{itemize}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Barcyentric Quadrature for $v''(x)$}
In order to simulate erosion, we require the deformation gradient which
means that a quadrature rule for $v''(x)$ is required.  Using the same
techniques that are used to compute $v(x)$ and $v'(x)$, a Barycentric
quadrature rule for the second derivative can be constructed using the
identities
{\color{red}
\begin{alignat}{3}
  0 &= \frac{1}{2\pi i}\int_{\Gamma} 
    \frac{2v^-({ y})-2v(x)-2(y-x)v'(x)-(y-x)^2v''(x)}{(y-x)^3} dy, &&x \in \Omega, \\
  0 &= \frac{1}{2\pi i}\int_{\Gamma}
    \frac{2v^+(y)-2v(x)-2(y-x)v'(x)-(y-a)^{-1}(x-a)(y-x)^2 v''(x)}
    {(y-x)^3} dy, \quad &&x \in \Omega^c.  \label{eqn:Identity}
\end{alignat}
and the quadrature formulations are
\begin{alignat}{3}
  v''(x) &\approx
    \frac{2\sum\limits_{j=1}^N \frac{v_j^- -v(x)-(y_j-x)v'(x)}{(y_j-x)^3}w_j}
    {\sum\limits_{j=1}^N \frac{1}{y_j-x}w_j}, &&x \in \Omega, \\
  v''(x) &\approx \frac{1}{x-a}\frac{2\sum\limits_{j=1}^N
    \frac{v_j^+ -v(x)-(y_j-x)v'(x)}{(y_j-x)^3}}{\sum\limits_{j=1}^N \frac{(y_j-a)^{-1}}{y_j-x}w_j}
    , \quad &&x \in \Omega^c.  \label{eqn:SecondBary}
\end{alignat}
where $a$ is a point inside the $\Omega$ in equations~\eqref{eqn:Identity} and \eqref{eqn:SecondBary}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Fast Summation Methods}
\label{sec:fmm}
{\color{red}
To numerically compute the completed double-layer potential, we discretize each of the $M$ bodies with  $N_\iin$ points, and the outer boundary with $N_\out$ points.
}
\begin{itemize}
  \item Apply trapezoid rule as a first pass

{\color{red} We use the Fast Multipole Method (FMM)~\cite{gre-rok1987, gre-gre-may1992} with trapezoid rule to calculate the double-layer potential.
}
  \item Efficiently find points that are too close for trapezoid

{\color{red}
 Let $L_w$ be the length of the outer boundary and $L_{b}$ be the length of the boundary of body where $b=1, \cdots, M$. Here are the criteria to see if two points are too close for trapezoid. For criterion of outer boundary to body,  let $d$ be the minimum distance between outer boundary and a point $x$ on the body $b$, we say $x$ is too close to wall if
$$d<\frac{L_{b}}{2\pi} + \alpha_1\frac{L_w}{N_\out}$$
where $\alpha_1$ is a constant. 
For criterion between two bodies, let $d$ be the distance between the centroid $a$ of the body $b_1$ and a point $x$ on the body $b_2$, we say they are too close if
$$d<\frac{L_{b_1}}{2\pi}+\frac{L_{b_2}}{2\pi}+\alpha_2\left(\frac{L_{b_1}}{N_\iin}+\frac{L_{b_2}}{N_\iin}\right)$$
where $\alpha_2$ is a constant.

}
  \item Subtract off trapezoid rule directly
  \item Add on Barycentric directly
\end{itemize}
{\color{red} Discussion of the choices of $\alpha_1$ and $\alpha_2$ with respect to accuracy and  efficiency?}
